Manuscript for MADA Project

### 2023-02-09 products/manuscript/Manuscript.qmd
Error found by Dr. Handel Fixed
Error caused by dplyr::summary(rawdata)

##Summary Descriptions of Data
```{r}
dplyr::glimpse(rawdata)
dplyr::summary(rawdata)
```

@@

##Important Notes
I have been downloading this data weekly since Septmember 17th and I will continue doing so until the end of the intervention in Albany.

>>>>

##Summary Descriptions of Data
```{r}
summary(rawdata)
```

@@

##Important Notes
I have been downloading this data weekly since September 17th and I will continue doing so until the end of the intervention in Albany.
